\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}                    
\moderncvcolor{blue}                       

% character encoding
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}

% personal data
\name{Zhengyang}{Yu}
\title{Curriculum Vitae}
\address{San Diego \& Bay Area}{}{}
\phone[mobile]{+1~510~754~7176}
\email{zhy079@ucsd.edu}
\email{zizha.work@outlook.com}
\social[github]{zizhaolaisuimuqu}
\social[linkedin]{zhengyang-yu-592a19309}
\homepage{resume.zizhaolaisuimuqu.top}
\extrainfo{\httplink{aboutme.zizhaolaisuimuqu.top}}\extrainfo{\href{https://aboutme.zizhaolaisuimuqu.top}{\textbf{More →}}}



\begin{document}
\makecvtitle

\vspace{-1.5em}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2025 -- Jun 2027}{Bachelor of Science in Computer Science}{University of California, San Diego}{San Diego, CA}{}{
Expected Graduation: June 2027
}

\cventry{2023 -- 2025}{Associate of Science in Computer Science}{Laney College}{Oakland, CA}{}{
% GPA: N/A
}

%----------------------------------------------------------------------------------------
%   PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\cventry{2023}{\textbf{Java Snake Game}}{Personal Project}{}{}{
\begin{itemize}
\item Developed a classic console-based Snake game using Java, implementing efficient algorithms for movement, collision detection, and scoring.
\item Utilized object-oriented design principles and version control (Git) to maintain clean, modular code.
\end{itemize}
}

\cventry{2024}{\textbf{Home Assistant Presence Plugin}}{Personal Project}{}{}{
\begin{itemize}
\item Built a Home Assistant plugin detecting real-time room occupancy using entry/exit sensor data.
\item Designed event-driven architecture integrating Python scripts and RESTful APIs for smart lighting automation.
\end{itemize}
}

\cventry{2025}{\textbf{HTML to ePub Converter}}{Personal Project}{}{}{
\begin{itemize}
\item Engineered a converter to transform HTML content into ePub format, implementing scalable parsing and metadata embedding.
\item Enhanced reliability and efficiency through structured error handling and modular component design.
\end{itemize}
}


%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
\cvitem{Programming}{Python, Java, C++, C}
\cvitem{Concepts}{Algorithms, Data Structures, Object-Oriented Design, Software Testing, Debugging}
\cvitem{Tools}{Git, Docker, VS Code, Linux, Fusion 360, Adobe Creative Suite}
\cvitem{Other}{Electronics prototyping and fabrication (UCSD Envision Makerspace)}

%----------------------------------------------------------------------------------------
%   ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{Activities}
\cvitem{2024--2025}{Computer Consultant, Oakland Public Library - Elmhurst Branch
\newline Supported community members with computer troubleshooting and taught basic software skills.}

\cvitem{2024}{Member, Laney College MESA Program
\newline Participated in STEM enrichment workshops, peer collaboration.}

\cvitem{2025--Present}{Member, UCSD Envision Makerspace
% \newline Collaborate on cross-disciplinary engineering projects and prototype design tools.
}

\end{document}
